%
% The first command in your LaTeX source must be the \documentclass command.
\documentclass[sigplan,screen]{acmart}

%
% defining the \BibTeX command - from Oren Patashnik's original BibTeX documentation.
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08emT\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
    
% Rights management information. 
% This information is sent to you when you complete the rights form.
% These commands have SAMPLE values in them; it is your responsibility as an author to replace
% the commands and values with those provided to you when you complete the rights form.
%
% These commands are for a PROCEEDINGS abstract or paper.
\copyrightyear{2018}
\acmYear{2018}
\setcopyright{acmlicensed}
\acmConference[SER574 '19]{SER574 ’19: Assignment 1}{January 20, 2019}{Phoenix, AZ}
\acmBooktitle{SER574 ’19: Assignment 1, January 20, 2019, Phoenix, AZ}
\acmPrice{15.00}
\acmDOI{10.1145/1122445.1122456}
\acmISBN{978-1-4503-9999-9/18/06}

%
% These commands are for a JOURNAL article.
%\setcopyright{acmcopyright}
%\acmJournal{TOG}
%\acmYear{2018}\acmVolume{37}\acmNumber{4}\acmArticle{111}\acmMonth{8}
%\acmDOI{10.1145/1122445.1122456}

%
% Submission ID. 
% Use this when submitting an article to a sponsored event. You'll receive a unique submission ID from the organizers
% of the event, and this ID should be used as the parameter to this command.
%\acmSubmissionID{123-A56-BU3}

%
% The majority of ACM publications use numbered citations and references. If you are preparing content for an event
% sponsored by ACM SIGGRAPH, you must use the "author year" style of citations and references. Uncommenting
% the next command will enable that style.
%\citestyle{acmauthoryear}

%
% end of the preamble, start of the body of the document source.
\begin{document}

%
% The "title" command has an optional parameter, allowing the author to define a "short title" to be used in page headers.
\title{Enabling Agile Through Teamwork}

%
% The "author" command and its associated commands are used to define the authors and their affiliations.
% Of note is the shared affiliation of the first two authors, and the "authornote" and "authornotemark" commands
% used to denote shared contribution to the research.
\author{Cecilia La Place}
\authornote{Both authors contributed equally to this research.}
\email{claplace@asu.edu}
\orcid{1234-5678-9012}
\author{Chiranjeevi Ramamurthy}
\authornotemark[1]
\affiliation{%
  \institution{Arizona State University}
  \streetaddress{7001 E Williams Field Rd}
  \city{Mesa}
  \state{Arizona}
  \postcode{85212}
}

%
% By default, the full list of authors will be used in the page headers. Often, this list is too long, and will overlap
% other information printed in the page headers. This command allows the author to define a more concise list
% of authors' names for this purpose.
\renewcommand{\shortauthors}{La Place and Ramamurthy}

%
% The abstract is a short summary of the work to be presented in the article.
\begin{abstract}
For more than a decade, the Agile development process has seeped into the lives of software developers and customers, changing the way projects are planned, how teammembers and teams interact, and how customers receive their product. Agile is a teamwork heavy process, demanding superb communication and technical skills to develop projects where requirements can change the flow of the project between sprints. Similiarly, large scale projects need to consider large team management and team communication, as well as using distinct architectures and designs. 
\end{abstract}

%
% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
% Please copy and paste the code instead of the example below.
%
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Software and its engineering~Software creation and management</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010575.10010755</concept_id>
  <concept_desc>Software and its engineering~Software development process management</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010553.10010554</concept_id>
  <concept_desc>Software and its engineering~Software development methods</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003083.10003095</concept_id>
  <concept_desc>Software and its engineering~Software development methods</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Software and its engineering~Software creation and management}
\ccsdesc[300]{Software and its engineering~Software development process management}
\ccsdesc{Software and its engineering~Software development methods}
\ccsdesc[100]{Software and its engineering~Software development methods}

%
% Keywords. The author(s) should pick words that accurately describe the work being
% presented. Separate the keywords with commas.
\keywords{agile, teamwork, design, architecture, software development process}

%
% This command processes the author and affiliation and title information and builds
% the first part of the formatted document.
\maketitle

\section{Introduction}
The nature of agile development allows for a collaborative development environment by involving customers as team members. The basis of all software development is planning out a project from start to end, but requirements are prone to change when considering the fluctuating world of technology. However, technology is rapidly expanding, and as a result, agile must also change to handle larger team sizes or handling multiple teams. While agile is great at handling change, a scaled implementation must still handle change by valuing the people involved, customers and developers \cite{Highsmith01}. Furthermore, it must still be reliant on what Cockburn and Highsmith call "responsive people and organizations" as well as "[focusing] on the talents and skills of individuals" \cite{Cockburn01}. 

To observe and analyze how agile has adapted to scaling technology and teams, we will first, discuss teams in agile and how they scale. Second, we will discuss the different architectures used alongside these projects and design considerations.


\section{Teams in Agile}
A single team in agile consists of the product owner, the scrum master, and the developers. Successful teams must "have a common focus, mutual trust, and respect," be "collarborative, but speedy [in their] decision-making process" and be adept at handling ambiguity \cite{Cockburn01}. The Agile Manifesto encourages these attributes by valuing customer collaboration and responding to change over contracts and plans \cite{Beck01}. Daily stand-ups incite communication, updating each other on task statuses, and conveying problems if they exist. Depending on the needs that follow the stand-up, the team will respond accordingly. For example, team members may pair up to get a difficult or time sensitive task done.

\subsection{Scaling Up Teams in Agile}
As projects scale up, so does the number of teams. When considering this in an agile environment, there is more work that must go into ensuring that teams themselves can collaborate effectively. This can be accomplished by being in the same location. However, teams across multiple locations must account for different cultures and providing as much communication as possible \cite{Joshi12}. Distance increases the potential for misunderstandings. Other recommendations include having a single product backlog as mentioned by Zalavadia \cite{Zalavadia16}, cross-team daily stand-ups (and other cross-team activities) as suggested by GSATech \cite{GSATech}, and having communities of practice as discussed by Crocker \cite{Crocker18}. Each of these suggestions tackles a potential problem in large scale agile practices from cultural disagreements, to knowledge silos, to miscommunication. Having a single product backlog allows all teams to see the whole picture, and see where work is needed. Cross-team activities allows for a deeper understanding of the project and each team's accomplishments and troubles. Finally, communities of practices creates a valuable way to share information about relevant topics from other perspectives.

\section{Design and Architecture in Agile}
\subsection{Architecture}

Constraints such as financial, regulatory, technical, or customer driven are some of the fundamental reasons for the failure of a well established organization if their agile process is not bounded by a fail-safe plan. In order to mitigate these issues, there is an emerging trend which explores the possibility of using Agile practices in order to manage traditional business functions.  \cite{SoftArchAgile} A particular scenario where this issue is well addressed is the Scaled Agile Framework (SAFe).

The SAFe introduces two distinct elements of Architecture critical to its success:
\begin{itemize}
\item {\verb|Emergent Design|}
\item {\verb|Intentional Architecture|}
\end{itemize}

The technical basis for development and the incremental implementation of initiatives are provided by \textit{Emergent Design}. To ensure the initiative continually delivers value, Emergent Design helps Designers and Architects to be highly responsive to ever-changing customers and stakeholders. At this juncture, architecture that is SAFe can be seen as a collaborative and interactive exercise through which the design element can emerge. 

\textit{Intentional Architecture} however, is a more traditional architecture where the performance and usability of the initiative is supported and enhanced by a set of well-defined and planned architectural initiatives. The severity and importance of the constraints, such as choice of technology platform, financial budget, etc is clearly visualized using this Intentional architecture.

The key to the success is the level of abstraction at which the balance of Emergent Design and Intentional Architecture occur. 

Agile requires architecture that supports how Agile practices deliver outcomes (value). This is achieved through a combination of a nimble reactive style of architecture supported by a more traditional and structured approach to rchitecture \cite{EnterpriseArch}
\subsection{Design}
In large teams, and multi-team projects, design plays a significant role. Design is often the center of a project, and finding the right design can be difficult. There is a risk of a project adapting to other development approaches if the initial step of "finding the right design" fails. Therefore, effective integration of design is needed. This kind of team integration is possible only if every single person in the team has a deep insight about the product and has prior experience. Extra work could be generated if a designer does not work closely with their team, thus leading to harmful silos of knowledge within the team(s). \cite{AgileDesignPrac}

Avoiding this is crucial when a cross-functional team is involved in developing a product for intended customers/shareholders. By including designers in the agile planning process and pairing them with a developer to share their knowledge, this detrimental problem can be avoided. Having a visible work flow across the entire project is also helpful for all to see and work from. This approach enables a collaborative view, rather than a traditional linear view, and encourages the flow of ideas. 
\section{Conclusion}
In conclusion, agile projects with multiple teams are heavily dependent on communication, collaborative cultures, and extra information resources. When scaling an agile team, it is absolutely necessary to ensure that the ongoing scaling process facilitates the scaling of the architecture. In terms of design, it is mandatory that designers have access to developers, and designs are visible to the entire team(s), in order to ensure project success.

%
% The next two lines define the bibliography style to be used, and the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{sample-base}

\end{document}